Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-08-05 paper/main.tex
revision of results

% intro
For the AO stimulus, we created eight $t$-contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind of
descriptive nouns.
% furniture: blurred border between groom and object
The category ``furniture'' (\texttt{furn}) was not included in one of the
contrasts as regressor if interest because it can be considered as an object or
geometry-defining structure of a room/locale.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created for negative
control purposes to test if increased activation in the PPA was correlated with
moment of cuts and therefore correlated with a possible change in the
soundscape.

\begin{table*}[t]
    \caption{Contrasts of parameter estimates for the analysis of
        the audio-only stimulus (AO).
\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m).
Contrast 1-8 aim to isolate the PPA.
Contrasts 9-13 serve as negative control at the moments of movie cuts
with possible changes of the audio tracks soundscape (see Table
\ref{tab:av-contrasts}).}

@@

\todo[inline]{Why done this way? Why is no. 1 the one?}
% intro
For the AV stimulus, we created five $t$-contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind of cuts.
% no control for frames content
Notably, this was done without an annotation of the visual content depicted in
the frame after each cut and thus without statistically controlling confounding
variables.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or settings tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved narrative
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is
greater when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% im Ergebnis
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}).

@@

\paragraph{alignment etc.}
% single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
We co-registered the subjects in two ways.
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
On the one hand, subject-specific BOLD T2* time series were anatomically aligned
via linear transformation to a subject-specific, study-specific T2* template.
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
On the other hand, time series were aligned via non-linear transformation to a
study-specific T2* group template.
% MNI152
This reference image was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

@@

\todo[inline]{at the moment I think it is better to report the primary contrast
fist and then report the stability of contrast; but that opinion changend twice
already, so here in the text stability of contrast is still reported first}

% summary of methods: AO
We used conventional GLM contrast to exploratorily investigate how the PPA
responds to auditory cues embedded in a naturalistic audio-only stimulus.
% summary of methods: AV
We compare these results to results to an audio-visual naturalistic stimulus and
to results from a dedicated visual localizer experiment.

@@

% why we did different contrasts
Despite having chosen a primary contrasts which we assumed to give the best
results, we created a variety of contrasts to test if our approach yielded
similar results across a variety of contrasts.

% results
The overlap of significant clusters of the 7 (well actually 8) contrast for the
audio-description, and 5 contrasts computed for the movie can be found in Figure
\ref{fig:stability-slices}.

% AO eight contrasts
For the analysis of the AO stimulus, we combined different event categories to
create eight contrasts that provided different amount of data/events and
decreasing congruency with the spatial layout hypothesis.
% results in PPA
Six of eight AO contrasts show significant bilateral clusters in anterior
regions of the group PPA overlap.\todo[inline]{which is temporal occipital
fusiform gyrus regarding to co-registered Harvard-Oxford Cortical Structural
Atlas}
% Precuneus = retrosplenial cortex ?
Six of eight contrasts show significant clusters in the ventral precuneus /
retrosplenial cortex (RSC).
% statement/answer
This suggest results are reproducible in a variety of contrasts and do not
depend on the design of one specific contrasts.

% AV intro
For the analysis of the AV stimulus, we created five contrasts for a cross-modal
comparison.
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% lingual gyrus
In three contrasts, these homologous clusters extend into the lingual gyri.
% RSC
Further, three contrasts show significant homologous clusters in the RSC.
% LOC
Lastly, four contrasts show significant homologous clusters in lateral occipital
cortices.
% statement/answer
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts. Nevertheless, results are sensible to the amount of
data used in the contrasts and it's congruency with the spatial layout
hypothesis.

\subsection{primary contrasts}
% intro
For the primary contrast of the AO and AV stimulus, we report results on a group
level, on an individual level. Finally, we compare individual results of the AO
stimulus to the dedicated localizer paradigm.

\todo{intro sentence regarding the primary contrasts}
% the contrast in detail
The primary $t$-contrast for the audio-description comparing geometry-related
nouns to non geometry-related nouns spoken by narrator (\texttt{geo, groom > all
non-geo} yielded six significant clusters (see Table \ref{tab:res-ao-group1},
Figure \ref{fig:group-slices}).
% PPA
First, two fall into the anterior part of the visual localizer group overlap
mask.
% location
They are located (in part) in the lingual gyrus, occipital and temporal fusiform
gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
that's what the Harvard-Oxford Atlas suggests, clusterss are at borders of the
areas}.
% precuneus
Second, the contrasts yielded two homologous clusters in the ventral precuneus extending into the retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital cortex.

% AV intro
For cross-modal comparison purposes, we also analyzed data from the audio-visual
movie.
% the primary contrast
The primary $t$-contrast for the movie comparing cuts to a new setting with cuts
to a familiar perspective (\texttt{vse\_new > vpe\_old}) yielded three
significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA + others.
And one one cluster spanning across the midline and comprising intracalcarine
and cuneal cortex, lingual gyrus and retrosplenial cortex, occipital fusiform
gyrus and temporal fusiform gyrus, and parahippocampal cortex bilaterally.
% LOC
Two homologous clusters are located in the superior lateral occipital cortex
(left bigger than right).

@@

\subsection{individual results}
% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects. \todo{maybe report reason here, too: which
subjects influence the group results the most? ``multiple localizer''?}
% results in both subject and group space
Time series of all subjects were analyzed both in subject space and group space.
% why
For better comparison of results across participants, we report results of the
analysis that was performed in group space (Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded z-maps of the primary AO
and AV $t$-contrast and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
z=-11 for all subjects).

% results in detail voxels of significant clusters in PPA ROI (and  RSC
% liberally)
% sub-01: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-02: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-03: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-04: PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
% sub-05: PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
% sub-06: PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
% sub-09: PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-14: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-15: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-16: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
% sub-17: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-18: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
% sub-19: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-20: PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer shows bilateral clusters in 12 subjects and unilateral
right clusters in two subjects (sub-04, sub-20).
% subjective threshold
Noteworthy, ROIs were assessed by \citep{sengupta2016extension} by visually
inspecting the unthresholded $z$-maps, and setting a subjectively best fitting
$z$-threshold to isolate the PPA.

% AO
In the current analysis of the AO stimulus, we find significant bilateral
clusters in nine subjects, and one significant cluster in the left hemisphere of sub-09.
% subj-04
In sub-04, two homologous clusters are apparent, where the dedicated localizer
yielded only one cluster in the right hemisphere.

% AV
For the AV stimulus, results show homologous clusters in five subjects, and
unilateral right clusters in seven subjects (of which one subjects also yielded
just a unilateral cluster in the dedicated localizer).
% difference to dedicated localizer
In sub-20 bilateral, where the dedicated localizer yielded only one cluster in
the right hemisphere

@@

\subsection{Bland-Altman-Plots}
% why
To better depict the agreement (and difference) between indivudal results of the
visual localizer and contrast 1 of the AO paradigm, we created
Bland-Altman-Plots (see Figure \ref{fig:bland-altman}).
% what do Bland-Altman-Plots show?
The plots for the 14 subjects show the mean of $z$-values of two spatially
corresponding voxels in unthresholded z-maps on the x-axis and the difference of
$z$-values of these two voxels on the y-axis (dedicated localizer minus AO
stimulus).
% masking
We constrained the number of voxels in three ways. Voxels were spatially
contrained to a) voxels in the occipital and temporal lobes (gray; using the
(probabilistic) Jülich Histological Atlas \citep{eickhoff2005toolbox,
eickhoff2007assignment}), b) voxels located in the PPA overlap of all subjects
(blue), and c) voxels in the individual PPA ROI(s)(red).
% what we can see
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (KDE plot for the x-axis).
% but
Values above the horizontal line depict voxels that show a higher z-value in the
dedicated localizer, values below the horizontal line depict voxels that show
higher z-values in the AO stimulus.

\todo[inlin]{concluding statement for the paragraph}

\todo[inline]{the plots are ``biased'' in the PPA mask in such a way that they
don't take into account that clusters are not 100 perc. congruent, meaning the
AO stimulus has voxels in regions that are outside of the individual PPA ->
probably bias to show higher values for the dedicated localizer (red voxels)}

@@

@@

\todo[inline]{MIH: discussion should primarily be anchored on the points the
    introduction concludes with. From my POV there is no need (and likely no
    space) to discuss results by stimulus type. Issue like different impact of
    attentional focus etc can be brought up in the joint paragraph that
    discussed how such a factor could have differentially impacted the results
    and if that would matter.}

@@

% following paragraphs in the discussion section starts by describing an area of weakness or strength of the paper.
% It then evaluates the strength or weakness by linking it to the
% relevant literature.

% Discussion paragraphs often conclude by describing a clever, informal way of perceiving the contribution or by discussing future directions that can extend the contribution.

% For example, the first paragraph may summarize the results, focusing on their meaning.

% The second through fourth paragraphs may deal with potential weaknesses and with how the literature alleviates concerns or how future experiments can deal with these weaknesses.

@@

%Step by step, the reader thus learns to put the paper’s conclusions into the right context.
We used two naturalistic stimuli + annotation + GLM and investigated if we could
isolate the PPA not just in an group average analysis but also on an individual
level. We focus on the audio-only stimulus but performed a analysis for the AV
stimulus as well (not controlling for frame content after cuts).

@@

% AV
On individual level, mixed results for AV stimulus.
% individual differences
Individual differences when seeing a whole picture with many features vs. stream
of serial auditory information providing incidential cues; spatial attention?
\todo[inlin]{which contrast works better in which subjects?}

@@

\subsection{shortcommings}

>>>>

% intro
For the AO stimulus, we created eight $t$-contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind of
descriptive nouns.
% furniture: blurred border between groom and object
We did not use the category ``furniture'' (\texttt{furn}) as a regressor in one
of the contrasts of interest because this category was considered to eighter
count as object or a geometry-defining structure of a room/locale.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created for negative
control purposes to test if increased activation in the PPA was correlated with
moments of cuts and therefore correlated with a possibly accompanying change in
the soundscape (anticipating the narrator's cue of a switch to new setting, too).

\begin{table*}[t]
    \caption{Contrasts of parameter estimates for the analysis of
        the audio-only stimulus (AO).
\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m.
Contrast 1-8 aim to isolate the PPA.
Contrasts 9-13 serve as negative control at the moments of movie cuts
with possible changes of the audio tracks soundscape (see Table
\ref{tab:av-contrasts}).}

@@

\todo[inline]{Why done this way? Why is no. 1 the one?}
% intro
For the AV stimulus, we created five $t$-contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind of cuts.
% no control for frames content
Notably, this was done without an annotation of the visual content depicted in
the frame after each cut and thus without statistically controlling confounding
variables.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is
greater when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% im Ergebnis
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}).

@@

\paragraph{alignment etc.}

\todo[inline]{give references to the publications explaining the template
creation; take a look at Sengupta (2016), and maybe speech-anno-paper}
% single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
We co-registered the subjects in two ways.
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
On the one hand, subject-specific BOLD T2* time series were anatomically aligned
via linear transformation to a subject-specific, study-specific T2* template.
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
On the other hand, time series were aligned via non-linear transformation to a
study-specific T2* group template.
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

@@

% summary of methods: AO
We used conventional GLM contrasts to exploratorily investigate if auditory cues
embedded in a naturalistic audio-only stimulus correlate with increased
hemodynamic activity in the PPA.
% summary of methods: AV
We compare these results on a group and individual level to results gained from
an audio-visual naturalistic stimulus and to results from a dedicated visual
localizer experiment.

@@

\subsection{primary contrasts}

\todo[inline]{at the moment I think it is better to report the primary contrast
fist and then report the stability of contrast; but that opinion changend twice
already.}

\todo[inline]{concluding statement for each paragraphs?}

% the contrast in detail
The primary $t$-contrast for the audio-description comparing geometry-related
nouns to non geometry-related nouns spoken by the narrator (\texttt{geo, groom >
all non-geo} yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% PPA
Two homologous clusters are located in the anterior part of the visual localizer
group overlap mask.
% location
More specifically, they are partially located in the lingual gyrus, occipital
and temporal fusiform gyrus, and posterior parahippocampal cortex \todo{the
    clusters are small but that's what the Harvard-Oxford Atlas suggests,
    clusters are at borders of the areas; dunno how to report this; sound shitty
to me}.
% precuneus
Two additional clusters are located in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, the contrast yielded two homologous clusters in the superior lateral
occipital cortex.

% AV intro
For cross-modal comparison purposes, we also analyzed data from the audio-visual
movie by contrasting different kinds of movie cuts independent from the frames'
visual content after the cuts.
% the primary contrast
The movie's primary $t$-contrast that compared cuts to a new setting with cuts
to a familiar perspective (\texttt{vse\_new > vpe\_old}) yielded three
significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA + others.
One cluster spanning across the midline comprising parts of the intracalcarine
and cuneal cortex, lingual gyrus and retrosplenial cortex, occipital fusiform
gyrus and temporal fusiform gyrus, and the parahippocampal cortex of both
hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

@@

\subsection{individual results}
% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects. \todo{maybe report the other reason here, too:
which subjects influence the group results the most? ``multiple localizer''?}
% results in both subject and group space
Time series of all subjects were analyzed both in subject space and group space.
% individual z-maps
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05) can be
found in the accompanying dataset.
% why
For better comparison of results across participants, we show results ($z$-maps;
Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in group
space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
z=-11 for all subjects).
% results in detail voxels of significant clusters in PPA ROI (and  RSC
% liberally)
% sub-01: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-02: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-03: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-04: PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
% sub-05: PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
% sub-06: PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
% sub-09: PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-14: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-15: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-16: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
% sub-17: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-18: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
% sub-19: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-20: PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer shows bilateral clusters in 12 subjects and unilateral
right clusters in two subjects (sub-04, sub-20).
% subjective threshold
Noteworthy, ROIs were assessed by \citep{sengupta2016extension} by visually
inspecting the unthresholded $z$-maps, and setting a subjectively best fitting
$z$-threshold to isolate a cluster in the PPA.
% AO
In the current analysis of the AO stimulus, we find significant bilateral
clusters in nine subjects, and one significant cluster in the left hemisphere of sub-09.
% subj-04
In sub-04, two homologous clusters are apparent, where the dedicated localizer
yielded only one cluster in the right hemisphere.
% AV
For the AV stimulus, results show homologous clusters in five subjects, and
unilateral right clusters in seven subjects (of which one subjects also yielded
just a unilateral cluster in the dedicated localizer).
% difference to dedicated localizer
In sub-20 bilateral, where the dedicated localizer yielded only one cluster in
the right hemisphere.

@@

\subsection{Bland-Altman-Plots}
% why
To better depict the agreement (and difference) between indivudal results of the
visual localizer and contrast 1 of the AO paradigm, we created one
Bland-Altman-Plots for each of the 14 subjects (see Figure
\ref{fig:bland-altman}).
% x-axis
The x-axis of every subplot depicts the mean of $z$-values of two spatially
corresponding voxels taken from a subject's unthresholded $z$-map.
% y-axis
The y-axis of every subplot depicts the difference of $z$-values of two
spatially corresponding voxels (dedicated localizer minus AO stimulus).
% masking
We constrained the number of voxels in three ways as indicated by three colors
(grey, blue, red).
% masking in detail
Voxels were spatially contrained to a) voxels located in the occipital and
temporal lobes (gray; using the (probabilistic) Jülich Histological Atlas
\citep{eickhoff2005toolbox, eickhoff2007assignment}), b) voxels located in the
PPA overlap of all subjects (blue), and c) voxels located in the individual PPA
ROI(s)(red).
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AO stimulus.

@@

% all AO contrasts
% 1 geo, groom > non-geo:               PPA (l/r); RSC (l/r)
% 2 geo, groom, se_new > non-geo:       PPA (l/r); RSC (l/r)
% 3 groom, se_new, se_old > non-geo:    PPA (l/r); RSC (l/r)
% 4 geo > all non-geo PPA               PPA (l/r); RSC (l/r)
% 5 groom > all non-geo PPA             PPA (l/r); RSC (l/r)
% 6 se_new > all non-geo PPA            PPA (l/r); RSC (l/r)
% 7 se_new, se_old > all non-geo PPA               RSC (l/r)
% 8 se_new > se_old                     nothing
% 9 vse_new > vpe_old                              RSC (r)
%10 vse_new, vpe_new > vse_old, vpe_old nothing
%11 vse_new > vse_old                   nothing
%12 vse_new > vse_old, vpe_old          nothing
%13 vse_new, vpe_new > vpe_old          nothing

% all AV contrasts
% 1 vse_new > vpe_old: big bilateral cluster in PPA but also RSC, visual c.
% 2 vse_new, vpe_new > vse_old, vpe_old:
% group results are more more confined here
% (but individual results were probably worse)
% 3 vse_new > vse_old: PPA (l/r)
% 4 vse_new > vse_old, vpe_old: PPA (l/r)
% 5 vse_new, vpe_new > vpe_old: PPA (l/r) but also visual c.
% 6 vno_cut > vse_new: nothing
% 7 vno_cut > vse_old: nothing
% 8 vno_cut > vse_new, vse_old: nothing
% 9 vno_cut > vpe_new, vpe_old: nothing
%10 se_new > se_old: right PPA

% why we did different contrasts
We created a variety of contrasts to test if our approach yielded
similar results across similar contrasts and if localization performance
decreases the further the contrasts deviate from the spatial layout hypothesis
\todo{and the less data we use}.

% results
The overlap of significant clusters of 8 contrast for the audio-description, and
5 contrasts computed for the movie can be found in Figure
\ref{fig:stability-slices}.

% AO eight contrasts
For the analysis of the AO stimulus, we combined different event categories to
create eight contrasts that provided different amount of data/events and
decreasing congruency with the spatial layout hypothesis.
% results in PPA
Six of eight AO contrasts show significant bilateral clusters in anterior
regions of the group PPA overlap.\todo[inline]{which is temporal occipital
fusiform gyrus regarding to co-registered Harvard-Oxford Cortical Structural
Atlas}
% Precuneus = retrosplenial cortex ?
Six of eight contrasts show significant clusters in the ventral precuneus /
retrosplenial cortex (RSC).
% statement/answer
This suggest results are reproducible in a variety of contrasts and do not
depend on the design of one specific contrasts.
% results get ``worse''
Further, the ability to functionally isolate the PPA decreases the more a
contrast depends on (just) using \texttt{se\_new} and \texttt{se\_old}
\todo{interpretation (-> discussion): this category is essentially filled with
    nouns from other cateogries but nevertheless primarily cueing a change of
    setting; setting changes are often anticipated by a change of soundscape,
meaning the narrator lagges behind; well, and the more a contrasts only relies
on these, the less data is available, because just two categories the more the
contrast depends on (just) using se\_new or se\_old}

% AV intro
For the analysis of the AV stimulus, we created five contrasts for a cross-modal
comparison.
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% lingual gyrus
In three contrasts, these homologous clusters extend into the lingual gyri.
% RSC
Further, three contrasts show significant homologous clusters in the RSC.
% LOC
Lastly, four contrasts show significant homologous clusters in lateral occipital
cortices.
% statement/answer
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts.

\subsection{crossmodal and negative controls}

\todo[inline]{shall results of these contrasts be reported as well? imo: the one
who says a) should say b), too. At the moment the contrasts are just listed in
the method section}

\todo[inline]{there are only two control contrasts that yield significant
    clusters: in AO stimulus using annotation of movie cuts (vse\_new >
    pe\_old): right RSC; and in the AV stimulus using annotation of the narrator
    (se\_new > se\_old): right PPA; this kinda suggest particpants use the
soundscape for re-orienting (which still might be a bold claim)}

@@

@@

% following paragraphs in the discussion section starts by describing an area of
% weakness or strength of the paper.  It then evaluates the strength or weakness
% by linking it to the relevant literature.

% Discussion paragraphs often conclude by describing a clever, informal way of
% perceiving the contribution or by discussing future directions that can extend
% the contribution.

% For example, the first paragraph may summarize the results, focusing on their
% meaning.

% The second through fourth paragraphs may deal with potential weaknesses and
% with how the literature alleviates concerns or how future experiments can deal
% with these weaknesses.

@@

%Step by step, the reader thus learns to put the paper’s conclusions into the
%right context.

\todo[inline]{taylor it to points mentioned in the introduction (full circle)}

\paragrap{intro}
We used two naturalistic stimuli + annotation + GLM and investigated if we could
isolate the PPA not just in an group average analysis but also on an individual
level. We focus on the audio-only stimulus but performed a analysis for the AV
stimulus as well (not controlling for frame content after cuts).

@@

% AV
On individual level, mixed results for AV stimulus.
% individual differences
Individual differences when seeing a whole picture with many features vs.
serialc auditory stream of information providing incidential cues; spatial attention?
\todo[inline]{which contrast works better in which subjects?}

@@

\subsection{shortcomings}
